\documentclass[12pt, right open]{memoir}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{matrix,chains,positioning,decorations.pathreplacing,arrows,automata}
\usetikzlibrary{shapes.geometric, calc, intersections}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{float}
\floatstyle{boxed}
\restylefloat{figure}

\graphicspath{data/images}

\usepackage{ifthen}
\setcounter{secnumdepth}{5}


\begin{document}

\chapter{POORAM NAKSHATRA Star 11}


POORAM, is represented by 2 bright stars in the back of the constellation of Simmam.  Vedic Seers saw these 2 stars as representing the "BACK LEGS OF A COT". These stars are known in modern astronomy as DELTA-LEONIS (ZOSMA) and THETA-LEONIS (CHERTAN).  With a visual magnitude of 2.56, Zosma is the brighter one. 

Its main symbol is the legs of a couch or bed. Some astrologers also use a SWINGING HAMMOCK as one of Pooram's symbols. 

Pooram relates to a time where we look for rest, relaxation and amusement after fulfilling our wordly duties and responsibilities.  The symbol of the legs of a bed relates to the beginning part of the relaxation process. A lot of scientists and researchers have found that the solution to a problem usually comes to them, not when they are actually working at the problem.  The solutions come in the period when we have taken our mind-off it and are in a state of complete relaxation.  

BHAGA, one of the 12 Adityas (solar deities) is the main ruling deity of this nakshatra.  Bhaga's name translates roughly into "DELIGHT", "PLEASURE" and "INDULGENCE".  That's why it is related to the planet Venus. 

Bhaga's strong relationship with enjoyment makes this as one of the most carefree nakshatras.  Pooram natives don't like to worry as they are comfortable, especially from a physical point of view.  

Pooram is directly connected to Shiva-Lingam, the most commonly worshipped form of Shiva.  

Pooram is considered to be a balanced nakshatra.  Pooram balances creativity with relaxation, work with pleasure, aggression with gentleness.

Pooram relays the brahminical side of the planet Venus.  SHUKRA CHARYA, the presiding deity of Venus, is the preceptor of the demons and has the unique distinction of knowing SANJIVINIVIDYA (knowledge of bringing the dead back to life), which even BRIHASPATI, the preceptor of the gods, does not possess. 

It is a Female nakshatra. Beauty, vanity, love of ease, comfort and luxury are all primarily female concerns.  

The SEX ORGANS, THE LIPS and THE RIGHT HAND are the body parts related to this nakshatra. It is a "PITTA" (fiery) nakshatra.

According to Varahamihira, Pooram borns "have sweet speech, pleasing manners, habit of wandering and often serve the government in one way or another.
The 1st paagam of Pooram indicates ego, dignity and regality;

The 2nd paagam of Pooram indicates the most sober and hardworking paagam;

The 3rd paagam of Pooram indicates the liking for travels, harmony, relaxation, refinement, counselling, creation and appreciation of beauty; 

The 4th paagam of Pooram indicates the emphasis on intensified emotions, home and family life. 


\section{Poorvaphalguni or Pooram Star or Nakshatra:}

You are expert in love making, strong and handsome, but extremely fearful. You help others, and carryout works which cannot be done by others. You are angry, fraud, cruel and candid. You are bright, wealthy, giver, expert in music and dance. You are wise and are in the government service. You are longlived and and be get few children. You are learned, reserved, handsome, love your brothers, endowed with soft hands and feet, born of Rajamsha, strict transactor, endowed with a attractive eyes, idle and possess government signs.

\section{Pooram fall in the 13-26 degrees of Leo }

\subsection {Male Natives}
Physical features:
He has attractive personality. A stout body with mixed color. Frequent sweating. A snubbed nose.


\subsection {Character and general events}
He likes full freedom. It is seen that the native becomes famous in one or the other field. However, his mind will be full of disturbances on one or the other matter. He has inherent intuitive powers to know the problems of others. Hence, even before the help is requested for, the native extends his helping hand to the needy. He has sweet speech. He is fond of travelling.

\subsection {Education and sources of earnings / profession}
He cannot be a slave to anybody. Because of this quality often noticed that he will not take up a job which involves subordination in its true meaning. There is a drawback in the native, that he cannot be a 'yes master' even to his boss in the case of employed persons. Hence he is not in a position to derive much benefit from his superiors.
He wants to be sincere in all the work he undertakes. Neither he can be a party to any illegal activities not has he the power of tolerance to see such activities. This condition of his mind drags him into several complications in life and he is ready to face such problems. He does not like to get any benefit at the cost of others pocket. There will be several hidden enemies to him. Hence, such enemies stand as a main obstacle in the progress. However, the native is able to crash such enemies and attain much success in all the work he undertakes. He is a power monger. He gives preference to the position and authority rather than money. He observes right path to the progress and may devote his valuable time for such a cause. Even though the native is able and intelligent he cannot reach the place where he thinks to be. It does not mean that the native will not rise in the life.
In the employment field, he will frequently change his job, particularly at the age of 22, 27, 30, 32, 37 and 44 years. He will attain the requisite position only after his 45th years of age. While he does not want other's money he will be frequently in trouble in the financial matters from others. In other words, borrowers will not return the money to him.
In spite of all the adverse positions mentioned above he, after his 45th years of age, will reach a good position where power and authority vests in him. In the business field he can shine well.


\subsection{Family life}
His married life will be happy. He will have good wife and children and also derive much happiness from them. In some cases it has been noticed that the native does not marry the girl of his choice. He will lead a life away from his native place and other family members.

\subsection{Health}
His health will generally be good. However, he is prone to dental disease, abdomen problem and diabetics. Even so, no permanent nature of disease is noticed in the native.

\section{Purva phalguni phalguni Nakshatra}
The arena of Purva Phalguni Nakshatra is the enclosure of Shivalinga deity beginning from 13.20 degrees as following till 26.40 degrees in Simha or Leo zodiac which is ruled by planet Venus and gives an expression of swinging hammock. The Poorva Phalguni arena comprises all the pleasures of supreme palace comprising amusements, love, happiness and sensual delights while on the other hand it also holds celibacy and asceticism as in further articulation it expresses creation as well as the end of it. This arena is the divine expression of fortune and fame.

\subsection{Reflections of Purva phalguni phalguni Nakshatr}

The natives of Purva Phalguni Nakshatra could be seen as the blend of all shades together including both negative and positive colors. They are timid personas but will do all those things which anybody else won’t do, they are provided with anger and callousness but they could also be seen helping others for being good at heart too. These people carry strong and handsome personality but are perceived to be flirts upon land. Their path of life is believed to be endowed with good wealth besides which they enjoy their lives but are learned and wiser personas too.

\subsection{Impacts/Results for Male natives born in Purva phalguni Nakshatra}

\subsubsection{Appearance of people of Purva phalguni nakshatra}
The male natives of Purva Phalguni Nakshatra are perceived to be bestowed with strong personas and dominating personality besides which they are endowed with handsome appearance which carries a strong appeal. These natives possess stout body with medium complexion along with snubbed nose. These people could be seen as frequently sweating.
 	 	
\subsubsection{Attitude and life path of natives of Purva phalguni nakshatra}
The natives of Purva Phalguni Nakshatra are perceived to be highly free living souls and would never stay in any sort of confinements. They won’t stay at a single place as they are travelers and so on would travel throughout life besides this, they would like to be confined in any relations as they strongly require their space there as well. These people possess a imbalanced mind with much fluctuations in their thoughts for which they won’t be able to take strong and firm decisions and so on he will lead a imbalanced life.

The individuals of Purva Phalguni arena are soft and kind at heart and are true helping personas as they could be helping many around besides which they are endowed with the strength of intuitions to know about others problems and needs which further makes them reach their needs sooner. Besides this, they are born with aggressive blend too and could also turn harsh and callous at times while they are believed to be soft at heart and sweet at their words.

The Purva Phalguni natives are born with coward inside and timid composure of mind but they appear completely opposite to the same as they could be seen doing many such thing which others might not do and so on makes them appear stronger.

\subsubsection{Professional front}

The free living blend of Purva Phalguni natives arises here also as these people  cannot stay in any compact confinement neither in office arena besides which they can’t stay under any supervision as in strict subordination  and this could become their weakness in the professional path besides which they cannot see anything going against what they feel is right even if they are the words of their superiors. In vivid articulation they would not stay as slaves at their work place.

These male natives of Purva Phalguni arena are perceived to be very sincere at work and pursue everything with complete honesty and on the other hand, they strongly expect the same from those around in their work arena. The natives of Poorva Phalguni Nakshatra  are not at the people of money as they only pour their concern upon strength and authority of profile. In further extension, these people of Poorva Phalguni Nakshatra won’t ever seek for any undeserving benefits from others as they will even leave those of their share. The won’t even ask their money back from whom they lend before and this all would bring them some difficulties in their life path as specially in finances.

On the other hand, being good enough, The natives of Poorva Phalguni Nakshatra are not fragile personalities as they would be surrounded by many enemies lurked around but they are potent enough to push them back and move further. These natives are bestowed with strong mount of good height but it won’t be equal to their efforts and intellect.

In the end, these natives would confront much fluctuations in their professional walk during the ages of 22, 27, 30, 32, 37 and 44years. They will reach their stronger and deserving place at the age of 45yrs and will grow further.

\subsubsection{Family portrait}

The family portrait of Purva  phalguni natives will shine with the shades of bliss and delight as their will be a happy married life where he would walk with a good wife and will have good children which altogether will make his conjugal path contented and satisfied. It has been believed that these natives of Poorva Phalguni Nakshatra would get married upon their parents or others choice due to variant reasons.

In the end, the only bit difficult side of this portrait is that the Purva Phalguni Nakshatra natives are perceived to spend their life quiet far from their family on account of variant reasons.

\subsubsection{Health}

The natives of Purva phalguni Nakshatra are endowed with healthy walk upon life path as their would be only few little problems he would confront which would include dental disease, abdomen problems and diabetics as well. The good part here is that none of health hurdles would be much stronger or heaver, neither they would stay for much long.
\end{document}