\documentclass[12pt, right open]{memoir}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{matrix,chains,positioning,decorations.pathreplacing,arrows,automata}
\usetikzlibrary{shapes.geometric, calc, intersections}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{float}
\floatstyle{boxed}
\restylefloat{figure}

\usepackage{ifthen}
\setcounter{secnumdepth}{5}


\begin{document}

\chapter{Intro}
Sevvai Dosham is also known as Guja Dosham or Guja Dosh. 

It is also known as Manglik or Manglik Dosh in the northern part of our country.

In a horoscope, if Sevvai (Mars in English and Mangal in Hindi) is in the 2nd, 4th, 7th, 8th or 12th houses from the Lagna or Chandran or Sukran, the horoscope is supposed to suffer from Sevvai Dosham.

A horoscope with Sevvai Dosham should not be considered as matching for marriage with a horoscope which does not suffer from Sevvai Dosham.

This is the general rule.  If a horoscope with Sevvai Dosham is married to a horoscope without Sevvai Dosham, it is feared that the life of the spouse will be endangered.

Now it need not necessarily be a demise.

In modern days, it can be taken the other way around also.  In the case of incompatible Sevvai Doshams, it may, instead of risking the life of the spouse, may result in a long term separation, legal separation (divorce) or frequently disrupted marital relationships, taking away the peace of mind.The conclusion need not necessarily be the demise of the spouse.

As we have seen earlier, a Sevvai Dosham is constituted if Sevvai is in the 2,4,7,8 or 12th house from the Lagna, Chandran or Sukran.

Sevvai Dosham is exempted under several conditions.  

In some cases there are varying versions of exemptions.  

But most of the exemptions are common in different versions.The following are the exemptions for Sevvai Dosham, even if Sevvai is in the 2nd, 4th, 7th, 8th or 12th houses from the Lagna, Chandran or Sukran. 

In the case of exemption to Sevvai Dosham, it should be taken as if the horoscope is not suffering from Sevvai Dosham, since the same is offset by the exemption.

\section{The exemptions are:}
1.  Whatever be the place of Sevvai in a horoscope, if Sevvai is in his exalted house (Uchcham) Makaram, or ruling houses (Aakshi houses) Mesham and Vrichigam, Sevvai Dosham is exempted.

2.  Wherever is Sevvai in a horoscope, if the Lagna of the horoscope is Katagam or Simham, Sevvai Dosham is exempted.

3.  Whatever is the place of Sevvai with reference to Lagna, Chandran or Sukran, if Sevvai is in Simham or Kumbam, Sevvai Dosham is exempted.

4.  If Sevvai is in Simham, Katagam, Dhanur or Meenam Raasis, Sevvai Dosham is exempted.

5.  If Sevvai is associated with Sani, Raahu or Kethu or if Sevvai is receiving the aspect (Paarvai) of Sani, Raahu or Kethu, Sevvai Dosham is exempted.

6.  If the Lord of the house where Sevvai is positioned in the horoscope, from where Sevvai Dosham is constituted, is either in Kendra Sthanas or Thri-Kona Sthanas, (1,4,5,7,9,10 houses), Sevvai Dosham is exempted.

7.  If Sevvai is associated with Guru or Chandran, Sevvai Dosham is exempted.

8.  If Sevvai is in the 2nd house from the Lagna or Chandran or Sukran, and if such a 2nd house happens to be Midhunam or Kanni, Sevvai Dosham is exempted.

9.  If Sevvai is in the 4th house from Lagna, Chandran or Sukran, and if such a house is Mesham or Vrichigam, Sevvai Dosham is exempted.  (In Mesham and Vrichigam, Sevvai Dosham is also exempted as a general rule.

10.  If Sevvai is in the 7th house and if the 7th house is Makaram or Katagam, Sevvai Dosham is exempted.

11.  If Sevvai is in the 8th house, and if the 8th house is Dhanur or Meenam, Sevvai Dosham is exempted.

12.  If Sevvai is in the 12th house, and if the 12th house is Thulam or Rishabham, Sevvai Dosham is exempted.

13.  If Sevvai is associated with Sooriyan or Budhan or aspected by Sooriyan or Budhan, Sevvai Dosham is exempted.

If - and only if - Sevvai in the 2nd, 4th, 7th, 8th or 12 house from Lagna, Chandran or Sukran, does not fall under any of the above exemptions, it should be conceived that the horoscope suffers from Sevvai Dosham.

Normally it is believed that a horoscope with Sevvai Dosham should be married only to a person with Sevvai Dosham.  Otherwise, it is feared to have an impact on the life of the spouse.

No one will dare risk the chances of life.  As such, it has not been tried otherwise - atleast as far as my knowledge goes.

Hence the concept of Sevvai Dosham has necessarily to be applied in all horoscopes matching as a social necessity..
\end{document}